Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-09 Manuscript/Tmatrix.tex
adding dBSE for H2

@@

%%% FIGURE 3 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 4 %%%
\begin{figure}
	\includegraphics[width=\linewidth]{BeH2_gap}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2_gap}
\end{figure}
%%% %%% %%% %%%

>>>>

%%% FIGURE 3 %%%
\begin{figure*}
	\includegraphics[width=0.4\linewidth]{H2_dBSE1}
	\hspace{0.1\linewidth}
	\includegraphics[width=0.4\linewidth]{H2_dBSE3}
	\caption{
	Error with respect to FCI for the lowest singlet (left) and lowest triplet (right) excitation energies of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed with and without dynamical correction at the BSE@$G_0W_0$ and BSE@$G_0T_0$ levels with the cc-pVTZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2_dBSE}
\end{figure*}
%%% %%% %%% %%%

@@

%%% FIGURE 4 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2}
\end{figure*}
%%% %%% %%% %%%

%%% FIGURE 5 %%%
\begin{figure}
	\includegraphics[width=\linewidth]{BeH2_gap}
	\caption{HOMO and LUMO quasiparticle energies as well as HOMO-LUMO gap (in \si{\eV}) of \ce{BeH2} as a function of the internuclear distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the BSE@$G_0W_0$ (blue) and BSE@$G_0T_0$ (red) levels with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:BeH2_gap}
\end{figure}
%%% %%% %%% %%%
